---
title: "As Snippets"
author: "kittipos sirivongrungson"
date: '2022-05-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
here::i_am("dev/as.Rmd")
library(here)
library(dplyr)
```

### Plan

-   Convert List <-> Snippet Tibble

```{r}
usethis::use_r("as")
rstudioapi::navigateToFile(here("tests/testthat/test-as.R"))
```


```{r ls_ex}
ls_ex <- list(
  hello = list(
    scope = "markdown",
    prefix = "hello",
    body = c("hello, there", "$0"),
    description = "Say Hello"
  ),
  world = list(
    prefix = "world",
    body = c("Hi","Hi", "Welcome to a new world!")
  )
) 

as_snippets_tbl(ls_ex)
```

```{r}
as_snippets_tbl(ls_ex) %>% 
  as.list()
```


## Generic: As Snippets Tibble

```{r as_snippets_tbl}
as_snippets_tbl <- function(x) {
  UseMethod("as_snippets_tbl")
}
```


### Method: As Snippets Tibble (from List)

```{r as_snippets_tbl.list}
as_snippets_tbl.list <- function(x) {
  
  # Validate
  validate_snippets_list(x)
  
  # If "scope" is not provided set to `NA`
  scope_x <- purrr::map(x, "scope")
  noscope_lgl <- purrr::map_lgl(scope_x, is.null)
  scope_x[noscope_lgl] <- NA_character_
  # If "description" is not provided set to `NA`
  desc_x <- purrr::map(x, "description")
  nodesc_lgl <- purrr::map_lgl(desc_x, is.null)
  desc_x[nodesc_lgl] <- NA_character_
  
  tbl <- tibble::tibble(
    snippet_name = names(x),
    scope = as.character(scope_x), # scope always length 1
    prefix = purrr::map(x, "prefix"),
    body = purrr::map(x, "body"),
    description = desc_x
  )
  # Set Class
  new_snippets_tbl(tbl)
  
}

as_snippets_tbl.list(ls_ex) 
```




### Methods: As Snippets Tibble (from Data Frame)


`as_snippets_tbl.data.frame`

```{r as_snippets_tbl.data.frame}
as_snippets_tbl.data.frame <- function(x) {
  
  colnms <- c("snippet_name", "scope", "prefix", "body", "description")
  # Validate that must have at least these 5 column names
  validate_snippets_tbl_colnms(x)
  # Flatten 
  tbl_flat <- x %>% 
    # Select 5 columns
    dplyr::select(dplyr::all_of(colnms)) %>% 
    # Unnest list columns (not effect non-list column)
    tidyr::unnest(c(prefix, body, description))
  
  # Packing
  ## Group by snippet_name` and `scope`
  tbl_grp <- tbl_flat %>% dplyr::group_by(snippet_name, scope) 
  
  ## Check One-value Duplicate At Body and Warn
  tbl_grp_mod <- tbl_grp %>% 
    dplyr::mutate(is_body_dubs = is_one_val_rep(body))
    
  is_body_dubs_all <- any(tbl_grp_mod[["is_body_dubs"]])
  dup_value_in_body <- unique(dplyr::filter(tbl_grp_mod, is_body_dubs)[["body"]])
  
  if(is_body_dubs_all) {
    cli::cli_alert_warning("Found repeating one value in {.field body}, I will choose only one of {.val {dup_value_in_body}}.")
  } 
  
  ## Summarized
  tbl_uniq_name  <- tbl_grp %>% 
    dplyr::summarise(
      dplyr::across(
        c(prefix, body, description), ~list(unique_if_all_same(.x))), 
      .groups = "drop"
      ) 
  
  tbl <- tbl_uniq_name %>% 
    # Set Names of elemental rows
    purrr::modify(~stats::setNames(.x, tbl_uniq_name[["snippet_name"]])) 
  
  # Add Class
  new_snippets_tbl(tbl)
  
}

as_snippets_tbl.data.frame(as_snippets_tbl(ls_ex)) %>% 
  as.list.data.frame()
```

```{r}
tibble(x = c("a", "b"), y = c(T, F)) %>% 
  filter(y)

tibble(x = c("a", "b"), y = c(T, F))[c(T, F), ][["x"]]
```



```{r}
as_snippets_tbl(ls_ex) %>% 
  tidyr::unnest(c(prefix, body, description)) %>% 
  as_snippets_tbl.data.frame() %>% 
  as.list()
```

```{r}
tbl_ex <- tibble::tibble(
  snippet_name = c(rep("hello", 2), rep("world", 2)),
  scope = "markdown",
  prefix = snippet_name,
  body = c("hello", "how are you", "Welcome !", "To a new world!"),
  description = NA
) 
tbl_ex

as_snippets_tbl(tbl_ex)
```


```{r}
tibble::tibble(
  snippet_name = c("hello", "world"),
  scope = c("markdown", NA),
  prefix = c("hello", "world"),
  body = list(c("hello, there", "$0"), "Welcome to a new world!"),
  description = c("Say Hello", NA)
) 
```


```{r}
snp_tbl1 <- tibble(snippet_name = c("A", "B"),
       scope = rep(NA, 2),
       prefix = c("ha", "go"),
       body = list(c("ha", "ha"), c("hello", "hello")),
       description = rep(NA_character_, 2))

as_snippets_tbl.data.frame(snp_tbl1) %>% 
  show_snip_vscode()
```


```{r}
as_snippets_tbl(ls_ex) %>% 
  tidyr::unnest(c(prefix, body, description)) %>% 
  group_by(snippet_name, scope) %>% 
  mutate(is_dup_body = is_one_val_rep(body))
```
### Methods: As Snippets Tibble (from `snippets_tbl`)

```{r as_snippets_tbl.snippets_tbl}
as_snippets_tbl.snippets_tbl <- function(x) {
  validate_snippets_tbl_colnms(x)
  x
}
```


### As List

`as.list.snippets_tbl`

```{r as.list.snippets_tbl}
as.list.snippets_tbl <- function(x, ...) {
  
  colnms <- c("snippet_name", "scope", "prefix", "body", "description")
  # Validate Column Names
  validate_snippets_tbl_colnms(x)
  # Check Duplicated Values
  if(any(duplicated(x[["snippet_name"]]))) cli::cli_abort("{.code snippet_name} must not have duplicated values.")
  

 ls_tp <- x %>% 
    # Select 5 columns
    dplyr::select(dplyr::all_of(colnms[-1])) %>% 
    # Set Names of elemental rows
    purrr::modify(~stats::setNames(.x, x[["snippet_name"]])) %>% 
    # To list & Transpose
    as.list.data.frame() %>% 
    purrr::transpose()
 
 # Remove `NA`
 lv1_has_na_lgl <- ls_tp %>% purrr::map_lgl(~any(is.na(.x)))
 if (!any(lv1_has_na_lgl)) {
   # No any `NA`
   ls_tp
 } else {
   # Has any `NA`
   ## Remove sub-list that has `NA`
   for (i in names(which(lv1_has_na_lgl))) {
     
     lv2_has_na_lgl <- is.na(ls_tp[[i]])
     
     for (j in names(which(lv2_has_na_lgl))) {
       
       ls_tp[[i]][j] <- NULL
      
     }
   }
   ls_tp
 }

}

as.list.snippets_tbl(as_snippets_tbl(ls_ex))
```

#### Howto: Assign `NULL` to Sublist

```{r}
snp_tbl1 <- tibble(snippet_name = c("A", "B"),
       scope = rep(NA, 2),
       prefix = c("hel", "go"),
       body = c("hello", "good bye"),
       description = rep(NA_character_, 2)) %>% 
  as_snippets_tbl() 

snp_tbl1 
```

```{r}
snp_ls_tp <- snp_tbl1 %>% 
    # Select 5 columns
    dplyr::select("scope", "prefix", "body", "description") %>% 
    # Set Names of elemental rows
    purrr::modify(~stats::setNames(.x, c("A", "B"))) %>% 
    # To list & Transpose
    as.list.data.frame() %>% 
    purrr::transpose()

snp_ls_tp

lv1_has_na_lgl <- snp_ls_tp %>% purrr::map_lgl(~any(is.na(.x)))
which(lv1_has_na_lgl)

# For Loop
snp_ls_tp[[1]] 
snp_ls_tp[["A"]] 

lv2_has_na_lgl <- snp_ls_tp[[1]] %>% is.na()
which(lv2_has_na_lgl)
# For Loop
snp_ls_tp[[1]]["scope"] <- NULL
snp_ls_tp[[1]]["description"] <- NULL

snp_ls_tp
purrr::assign_in(snp_ls_tp, list("A", "description"), NULL)
purrr::assign_in(snp_ls_tp, c(1, 4), NULL)
```






```{r}
list(
  hello = list(
    scope = "markdown",
    prefix = "hello",
    body = c("hello, there", "$0"),
    description = "Say Hello"
  )
) %>% 
  as_snippets_tbl() %>% 
  as.list()
```


Error Cases

```{r}
as.list.snippets_tbl(iris)
as.list.snippets_tbl(as_snippets_tbl(ls_ex)[c(1,1), ])
```





Unnest Loose Class !!
 
 
```{r}
as_snippets_tbl(ls_ex) %>%
  tidyr::unnest(prefix:description) %>% class()
```




Name vector according to `snippet_name` and transpose

```{r}
as_snippets_tbl(ls_ex) %>% 
  # Set Names
  purrr::modify(~setNames(.x, c("hello", "world"))) %>% 
  # To list & Transpose
  as.list.data.frame() %>% 
  purrr::transpose() %>% 
  jsonlite::toJSON(pretty = T)
```



transpose named vector

```{r}
tibble(x = c(a = "a",b = "b")) %>% 
  as.list.data.frame() %>% 
  purrr::transpose()
```



```{r}
as_snippets_tbl(ls_ex) %>% 
  select(scope:description) %>% 
  as.list.data.frame() %>% 
  purrr::transpose()
```




### Helper: Flatten list if elements is Length 1 (Not In USE)

```{r flat_chr_if_len1}
flat_chr_if_len1 <- function(x) {
  
  stopifnot(is.list(x))
  # Check if every elements of list has length 1
  elements_len1 <- all(purrr::map_int(x, length) == 1L)
  
  if(elements_len1) {
    purrr::flatten_chr(x)
  } else {
    x
  }
}

flat_chr_if_len1(list("a", "b", NA))
flat_chr_if_len1(list("a", c("b", "c")))
```


```{r}
list("a", "b", NA) %>% map_int(length)

list("a", "b", NA) %>% flatten_chr()
list("a", c("b", "c")) %>% flatten_chr()
```



```{r}
names(list(1:2, c("a")))
names(list(a = 1:2, c("a")))

any(is.null(name(ls)), names(ls) == "")


purrr::map(ls_ex, names)
purrr::every(ls_ex, ~all(c("prefix", "body") %in% names(.x)))

purrr::map(ls_ex, "scope") %>% map_lgl(is.null)
purrr::map(ls_ex, "scope")[c(F, T)]
purrr::map(ls_ex, "description")
purrr::map_chr(ls_ex, "scope")
```








