---
title: "Build R Package"
author: "Your Name"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(eval = FALSE)
here::i_am("dev/build.Rmd")
library(here)
```

# How To

Essential Manuals and Packages:

-  [R Package Book](https://r-pkgs.org)
-  [usethis](https://usethis.r-lib.org)

I recommend initial setup by running the code that is not comment. Then, run the other commented code when you're ready.

# Git

```{r use_git}
usethis::use_git()
```

# Ignore

## Git Ignore

Tell Git not to track theses:

```{r use_git_ignore}
usethis::use_git_ignore("/dev/") # (Optional) ignore `dev` folder at PKG root
# usethis::use_git_ignore("file") 
```

## Build Ignore

Tell R not to build theses into R package:

```{r use_build_ignore}
usethis::use_build_ignore("dev") # (Require) if you use this template
# Testing VS Code Snippet
usethis::use_build_ignore("snippets")
```

# Metadata

## DESCRIPTION

```{r use_description}
# usethis::use_description()
```

## LICENSE

Use licence file by `use_*_license()` family of functions

```{r license}
usethis::use_mit_license() # MIT
```

# User Doc

## README

```{r readme}
# usethis::use_readme_rmd()
```

Lifecycle badges

```{r lifecycle_badge}
# usethis::use_lifecycle_badge("experimental")
```

## Vignette

```{r vignette}
# usethis::use_vignette("PKG")

## Articles
# usethis::use_article()
```

## NEWS

```{r news}
# usethis::use_news_md()
```


# Dependencies

## Imports

A recommended approach

```{r imports}
usethis::use_pipe() # If package use `%>%`
usethis::use_tibble() # If package use `tbl_df` class

usethis::use_package("fs") 
usethis::use_package("cli") 
usethis::use_package("tibble") 
usethis::use_package("purrr") 
usethis::use_package("dplyr") 
usethis::use_package("tidyr") 
usethis::use_package("jsonlite") 
```

```{r imports_dev}
## Developmental Package (not on CRAN)
# usethis::use_dev_package("pkg", remote = "OWNER/REPO")
```

## Import from

Importing a function from another package allows you to refer to it without a namespace (e.g., `fun()` instead of `package::fun()`).

```{r import_from}
# usethis::use_import_from("rlang", ":=") # Must have if use `:=`
```

## Suggests

Use suggested packages for example datasets, to run tests, build vignettes, or maybe there’s only one function that needs the package.

```{r suggests}
# usethis::use_package("pkg", type = "Suggests")
```

# Functions

Write some R functions!

```{r}
# usethis::use_r("fun1")
# usethis::use_test("fun1")
```


# Testing

## testthat

```{r use_testthat}
usethis::use_testthat()
```

Helper function for testing can be place in `tests/testthat/helper-tests.R`

```{r}
# fs::file_create(here("tests/testthat/helper-tests.R"))
```

## Package Coverage (Local)

See [covr](https://covr.r-lib.org)

```{r}
# covr::package_coverage()
```

for interactive use in viewer pane:

```{r}
# covr::report()
```



# Data

## Exported Data

-   `usethis::use_data()`: To store exported data in `data/`. 
Each file in this directory should be `.rda` file containing a single object.

-   `usethis::use_data_raw()`: To store code that used for data preparation in `data-raw/` 


```{r exported-data}
# usethis::use_data(data1) 

# usethis::use_data_raw("data1") # Code to prepare data
```


**Documenting datasets**

Document the name of the dataset in `R/` as roxygen2:

```{r data-doc-example}
#' Prices of 50,000 round cut diamonds.
#'
#' A dataset containing the prices and other attributes of almost 54,000
#' diamonds.
#'
#' @format A data frame with 53940 rows and 10 variables:
#' \describe{
#'   \item{price}{price, in US dollars}
#'   \item{carat}{weight of the diamond, in carats}
#'   ...
#' }
#' @source \url{http://www.diamondse.info/}
"diamonds"
```



## Internal Data

Save all of the objects for internal use in `R/sysdata.rda.`. They don’t need to be documented.

```{r internal_data}
# usethis::use_data(int_data1, int_data2, internal = TRUE)
```

## Raw Data

If you want to show examples of loading/parsing raw data, put the original files in `inst/extdata`.

```{r}
usethis::use_directory("inst/extdata")

usethis::use_directory("inst/extdata/vscode") # VS Code Snippets
```

Copy `meet.code-snippet`

```{r}
fs::file_copy(here("snippets/vscode-snippets/.vscode/meet.code-snippets"),
              here("inst/extdata/vscode")
              )
```

Copy `r.code-snippets`

```{r}
fs::file_copy(here("snippets/vscode-snippets/.vscode/r.code-snippets"),
              here("inst/extdata/vscode")
              )
```


```{r}
## Write Raw Data
# readr::write_csv(mtcars, here("inst/extdata/mtcars.csv"))
```




**Function: Get Path to Example Data**

This function allows user to access paths to raw data. 

Inspired from [readr example](https://github.com/tidyverse/readr/blob/HEAD/R/example.R).

```{r}
usethis::use_r("example") # Create `example.R` to store `PKG_example()`
usethis::use_test("example")
```

- Copy this `PKG_example()` to `example.R`, replace `PKG` with your package name.

``` r 
#' Get path to PKG example
#'
#' PKG comes bundled with a number of sample files in its `inst/extdata`
#' directory. This function make them easy to access
#'
#' @param file Name of file. If `NULL`, the example files will be listed.
#' @export
#' @examples
#' library(PKG)
#' PKG_example()
#' PKG_example("file.csv")
PKG_example <- function(file = NULL) {
  
  if (is.null(file)) {
    dir(system.file("extdata", package = "PKG"))
    
  } else {
    system.file("extdata", file, package = "PKG", mustWork = TRUE)
  }
  
}
```


# Template

Add an R Markdown Template

```{r use_rmarkdown_template}
# usethis::use_rmarkdown_template(
#   template_name = "Template Name",
#   template_dir = "dir-name",
#   template_description = "A description of the template",
#   template_create_dir = FALSE
# )
```

See also:

-   [Create Rmd Templates](https://rstudio.github.io/rstudio-extensions/rmarkdown_templates.html)


# Global Var

If R CMD Check shows a message like:

    Undefined global functions or variables:
      var1 var2
      
Put this:

```r 
# Declare global variables 
if(getRversion() >= "2.15.1")  utils::globalVariables(c("var1", "var2"))
```

in the same file as where you have package-level documentation.

```{r}
rstudioapi::navigateToFile(here("R/snipper-package.R"))
```

See this [Discussion](https://github.com/STAT545-UBC/Discussion/issues/451)


# CI workflow

Github action to automate R Package workflow. 

[Learn more](https://orchid00.github.io/actions_sandbox/)

## R-CMD-check

Github action to run R CMD Check in the cloud.

This will 

1. Create a YAML file: `.github/workflows/R-CMD-check.yaml`

2.  Adding R-CMD-check badge to 'README.Rmd'

```{r gha-check-release}
## Quickstart CI workflow
# usethis::use_github_action_check_release()
```

Ref: [Quickstart WF](https://github.com/r-lib/actions/tree/v1/examples#quickstart-ci-workflow)

## Test Coverage

1. Call `usethis::use_coverage()`

```{r use_coverage}
# usethis::use_coverage()
```

2. Use github action `test-coverage` 

This will connect your package to codecov.

```{r gha-test-coverage}
# usethis::use_github_action("test-coverage")
```

Ref: [test coverage WF](https://github.com/r-lib/actions/tree/v1/examples#test-coverage-workflow)


3. Click on codecov badge in README, it will open codecov site, then copy token to clip board, and paste the token and run:

```{r}
# covr::codecov(token = "your-token")
```


