---
title: "Planning for snipper"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # Set WD to Root
here::i_am("dev/plan.Rmd")
library(here)
```

Nomenclatures: DEV (for developer), USER (for user)

## Package Structure

-   **inst/**

    -   **rmarkdown/**

        -   RStudio RMD Template 1

    -   **templates/**

        -   Template

### Create Structures

```{r}
# fs::file_create(here("path"))
```

## OOP

**snippets_tbl**

-   attributes: "attr_name" = description

### Class Functions (DEV)

**snippets_tbl**

-   `create_snippets_tbl*`: create "snippets_tbl" & set ... attribute
-   `new_snippets_tbl()`: add "snippets_tbl" class to existing "tbl_df" class
-   `is_snippets_tbl*`: check class

**snippets_list**

-   `new_snippets_list()`: add "snippets_list" class to existing "list"

## Plan: USER functions

1.  `fun1`:

2.  `fun2`:

## Plan: ... functions Family

1.  `fun1`:

2.  `fun2`:
