---
title: "Body of Snippets"
author: "kittipos sirivongrungson"
date: '2022-05-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
here::i_am("dev/vs-body.Rmd")
library(here)
library(dplyr)
library(stringr)
```

## Tabstops

### Tabstops Example

```{r tabstop_ex1}
tabstop_ex1 <- "Hi $1 everyone ${2} now ${3:Goodbye} $ {fake} choose ${4|one,two,three|} ${5:nested ${6:placeholder}} \\$"

writeLines(tabstop_ex1)
```

```{r tabstop_ex1_ts}
tabstop_ex1_ts <- str_extract_tabstops(tabstop_ex1)[[1]]
tabstop_ex1_ts
```



### Extract Tabstops

```{r}
vs_meet_tbl$body$welcome
str_extract_tabstops(vs_meet_tbl$body$welcome)
```


```{r}
vs_meet_tbl %>% 
  mutate(tabstops = map(body, str_extract_tabstops)) %>% 
  pull(tabstops)
```




### Fun: Make Tabstops

Must provide `locations`

if `choices` is supply, ignore `placeholder` and `variables`.
 
`variables` can be supply with or w/o `placeholder` 

```{r tabstops_make}
tabstops_make <- function(locations, 
                            placeholder = NULL, 
                            choices = list(), 
                            variables = NULL
                            ) {
  
  is_simple <- is.null(placeholder) && length(choices) == 0 && is.null(variables)
  
  ## Helper Functions
  emBraces <- function(x) paste0("${", x, "}") 
  colonBraces <- function(lhs, rhs) emBraces(paste0(lhs, ":", rhs))
  
  # Simple
  if(is_simple){ return(emBraces(locations)) }
  
  # Choices
  if(length(choices) >= 1) {
    
    # Validate List
    if(!is.list(choices)) stop("`choices` must be a list of character vectors.")
    
    choices_laps <- purrr::map_chr(choices, ~paste(.x, collapse = ","))
    out <- emBraces(paste0(locations, "|", choices_laps, "|"))
    return(out)
    
  }
  
  # Variable
  if(!is.null(variables)) {
    
    out <- if(is.null(placeholder)) { 
      # With Placeholder
      emBraces(variables)
    } else {  
      # W/O Placeholder
      colonBraces(variables, placeholder)
    }
    
    return(out)
    
  }
  
  # Placeholder
  if(!is.null(placeholder)) {
    out <- colonBraces(locations, placeholder)
    return(out)
  }
  
}

tabstops_make(1:3)
tabstops_make(1, 
                choices = list(letters[1:3], c("Hello","hello")))
tabstops_make(1:2, placeholder = c("A", "B"))
tabstops_make(1, variables = "TM_SELECTED_TEXT")
tabstops_make(1, variables = "TM_SELECTED_TEXT", placeholder = "HI")
```

**Placeholders**
  
```{r}
loc_ex1 <- 1:3
ph_ex1 <- c("Hello", "Goodbye", "Hi")
paste0(loc_ex1, ":", ph_ex1)
```
  
**Choices**

```{r}
choice_ex1 <- list(c("one", "two", "three"), c("A", "B"))

paste0("|", paste(choice_ex1[[1]], collapse = ","), "|")
paste0("|", paste(choice_ex1[[2]], collapse = ","), "|")
```



### Fun: Extract Tabstops Elements

```{r str_extract_tabstops}
str_extract_tabstops <- function(string) {
  
  # Regex adapted from: <https://stackoverflow.com/a/41749376/13775646>
  reg_tabstops <- "(?<!\\\\)\\$(\\d+|\\{(?>[^{$}]|(?R))*\\})"
  str_extract_all_perl(string, reg_tabstops)
  
}
```

```{r}
tabstop_ex1

str_extract_tabstops(tabstop_ex1)
str_extract_tabstops(c("${1:Hello} $2", "${1:Hey}"))
```



### Helper: Str Extract All PCRE

```{r str_extract_all_perl}
str_extract_all_perl <- function(string, pattern) {
  
  matched <- gregexpr(pattern, string, perl = TRUE)
  
  out <- vector("list", length(string))
  
  for (i in seq_along(string)) {
    
    s <- string[[i]]
    m <- matched[[i]]
  
    out[[i]] <- substring(s, m, m + attr(m, "match.length") - 1)
    
  }
  
  names(out) <- names(string)
  out
  
}

str_extract_all_perl(c(a = "x1", b = "x2 x3"), "\\d+")
```


```{r}
ss <- c("x1", "x2 x3")
matched <- gregexpr("\\d+", ss, perl = TRUE)

substring(ss[1], matched[[1]], matched[[1]] + attr(matched[[1]], "match.length") - 1)

substring(ss[2], matched[[2]], matched[[2]] + attr(matched[[2]], "match.length") - 1)
```



### Howto: Extract `{}` and content


```{r}
tabstop_ex1

matched <- gregexpr("(?<!\\\\)\\$(\\d+|\\{(?>[^{$}]|(?R))*\\})", 
                    tabstop_ex1, perl = TRUE)
substring(tabstop_ex1, matched[[1]], matched[[1]] + attr(matched[[1]], "match.length") - 1)
```


```{r}
s <- "asf {GETME} asdf {HI {AGAIN} YO}"

matched <- gregexpr("\\{(?>[^{}]|(?R))*\\}", s, perl = TRUE)
substring(s, matched[[1]], matched[[1]] + attr(matched[[1]], "match.length") - 1)
```



```{r}
s <- "ass (as) sdf (ff) (a(s))d"

matched <- gregexpr("\\((?>[^()]|(?R))*\\)", s, perl = TRUE)
substring(s, matched[[1]], matched[[1]] + attr(matched[[1]], "match.length") - 1)
```



```{r}
s <- c("ass (as) sdf (ff) asd")
matched <- gregexpr("a", s, perl = TRUE)
substring(s, matched[[1]], matched[[1]] + attr(matched[[1]], "match.length") - 1)
```


From [stackoverflow](https://stackoverflow.com/a/41749376/13775646)

```{r}
s = "(a(a(a)(aa(a)a)a)a)((b(b)b)b)(((cc)c)c)"

matched <- gregexpr("\\((?>[^()]|(?R))*\\)", s, perl = T)
substring(s, matched[[1]], matched[[1]] + attr(matched[[1]], "match.length") - 1)
```



### Howto: Extract `$`

Extract `$` that is not come after `\\` (ignore `\\$`)

```{r}
reg_tab_dollar <- "(?<!\\\\)\\$"
tabstop_ex1 %>% str_extract_all(reg_tab_dollar)
```


```{r}
"\\$ a $" %>% str_extract_all("\\\\")
"\\$ a $" %>% str_extract_all("(?<!\\\\)\\$")
```

