---
title: "Read VS Code Meet Snippet"
author: "kittipos sirivongrungson"
date: '2022-05-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
here::i_am("dev/vs-meet.Rmd")
library(here)
library(jsonlite)
library(dplyr)
library(tibble)
library(purrr)
```

## Plan

JSON file -> List -> Tibble (Central format) -> List -> `json` class -> JSON file


-   Read `meet.code-snippets` from JSON to List

-   Convert it to tibble format (2 rows) each rows corresponding to one snippet

-   Convert tibble -> list then `toJSON` and write file


## Read from JSON to List

```{r vs_meet_ls}
vs_meet_ls <- jsonlite::fromJSON(
  here("snippets/vscode-snippets/.vscode/meet.code-snippets")
  )
```

```{r}
str(vs_meet_ls)
```

## List to Tibble

This will be a shared central format:

```{r vs_meet_tbl}
vs_meet_tbl <- tibble(
  snippet_name = names(vs_meet_ls),
  scope = map(vs_meet_ls, "scope"),
  prefix = map(vs_meet_ls, "prefix"),
  body = map(vs_meet_ls, "body"),
  description = map(vs_meet_ls, "description")
)

vs_meet_tbl
```

```{r}
vs_meet_tbl$scope
```


#### Howto: subset 2nd depth elements

```{r}
vs_meet_ls %>% map("scope") 
vs_meet_ls %>% map("prefix")
```

#### Howto: store list in a tibble 

```{r}
tibble(
  a = c("A", "B"),
  b = list(B = c("B", "C"), B = c("E")),
  c = list(C = c("D", "E", "F"), C = c("J"))
) 
```


## Manipulate Tibble Snippet

```{r}
vs_meet_tbl$body
```

Update $body of "welcome"

```{r vs_meet_tbl_mod}
vs_meet_tbl_mod <- vs_meet_tbl %>%
  rows_update(
    tibble(
      snippet_name = "welcome",
      body = list(welcome = c("Hi ${1:everyone}", "Welcome to the meeting"))
    )
  )

vs_meet_tbl_mod
```



## Tibble back to List


```{r vs_meet_ls_again}
vs_meet_ls_again <- vs_meet_tbl_mod %>% 
  select(-snippet_name) %>% 
  as.list() %>% 
  purrr::transpose(.names = vs_meet_tbl_mod$snippet_name)

vs_meet_ls_again
```


## List to JSON

```{r vs_meet_json_out}
vs_meet_json_out <- toJSON(vs_meet_ls_again, pretty = TRUE)
vs_meet_json_out
```


Looks OK

```{r}
vs_meet_json_out %>% 
  writeLines(here("snippets/vscode-snippets/.vscode/out/meet-out.code-snippets"))
```



